Modelling BCG vaccination in the UK

### 2019-07-16 rmds/05-evidence-policy-change.Rmd
corrected chapter structure
updated table positions

I recreated a previous approach for estimating the impact of ending the BCG schools scheme in England and Wales, updating the model with parameter uncertainty, and measurement error. I investigated scenarios considered by the Joint Committee on Vaccination and Immunisation, and explored new approaches using notification data (see Chapter \@ref(data)). I estimated the number of vaccines needed to prevent a single notification, and the average annual additional notifications caused by ending the BCG schools’ scheme. This work was supervised by Hannah Christensen and Ellen Brooks-Pollock.

@@

The effectiveness of the BCG vaccine was originally estimated by an MRC trial in 1953 at 80% in the United Kingdom [@Hart1972]. As follow up to this trial members of the MRC bio-statistics unit conducted a series of notification surveys attempting to ascertain any change in effectiveness, as well as acting as an estimate of notification rate across different demographics.[@Sutherland1987a] Notification surveys were carried out at 5 year intervals in 1973, 1978 and 1983; looking at those aged 15-24 years old in England and Wales. For the 1983 survey records of BCG status, Tuberculin status and ethnicity were extracted from the records of notifying physicians and the records of the local health and education authorities. Totals, across the study period, were then aggregated for the following group; Tuberculin negative and BCG positive, Tuberculin negative and BCG negative, Tuberculin positive and not vaccinated and those who did not participate. These totals were then combined with the population estimates for each cohort at 13 years of age to estimate the ethnic make up of the population, and to construct notification rates for each category. Data drawn from a range of sources including: Office of National Statistics data; annual local authority returns for total tuberculin test results; BCG vaccinations in the schools' scheme; and the Labour force survey (1983),

@@

For each scenario, I ran the model until 2028 with 10,000 parameter samples. I tested the difference between scenarios using the Mann-Whitney test for both the number of vaccines needed to prevent a single case in 15 years after vaccination for a cohort aged 13-14 years old at vaccination and the total number of additional notifications caused by ending the BCG schools' scheme. As in [@Sutherland1989] a 15 year time horizon was used with 5 year intervals. The year closest to the year of the change in vaccination policy (2005), which had model estimates, was used as the baseline.

@@

The model produced results that were comparable with those from [@Sutherland1989] (Table \@ref(tab:model_validation); Table \@ref(tab:model_validation-2)). When estimating the total notifications from ending the BCG schools' scheme at different times in ethnic White UK born adults aged 15-29 years old in England and Wales the model had a median absolute error of `r median_lll_hhh_error` and a maximum absolute error of `r {pretty_max}` when compared to [@Sutherland1989]. I found that the percentage of cases in the first year was $f=0.764$ when fitted to the Sutherland et al. estimates using the least squares method.

@@

# Discussion

>>>>

I recreated a previous approach for estimating the impact of ending the BCG schools scheme in England and Wales, updating the model with parameter uncertainty, and measurement error. I investigated scenarios considered by the Joint Committee on Vaccination and Immunisation, and explored new approaches using notification data (see Chapter \@ref(data)). I estimated the number of vaccines needed to prevent a single notification, and the average annual additional notifications caused by ending the BCG schools’ scheme. This work was adapted from a preprint^[Preprint: https://doi.org/10.1101/624916] supervised by Hannah Christensen and Ellen Brooks-Pollock.

@@

The effectiveness of the BCG vaccine was originally estimated by an MRC trial in 1953 at 80% in the United Kingdom [@Hart1972]. As follow up to this trial members of the MRC bio-statistics unit conducted a series of notification surveys attempting to ascertain any change in effectiveness, as well as acting as an estimate of notification rate across different demographics.[@Sutherland1987a] Notification surveys were carried out at 5 year intervals in 1973, 1978 and 1983; looking at those aged 15-24 years old in England and Wales. For the 1983 survey records of BCG status, Tuberculin status and ethnicity were extracted from the records of notifying physicians and the records of the local health and education authorities. Totals, across the study period, were then aggregated for the following group; Tuberculin negative and BCG positive, Tuberculin negative and BCG negative, Tuberculin positive and not vaccinated and those who did not participate. These totals were then combined with the population estimates for each cohort at 13 years of age to estimate the ethnic make up of the population, and to construct notification rates for each category. Data drawn from a range of sources including: Office of National Statistics data; annual local authority returns for total tuberculin test results; BCG vaccinations in the schools' scheme; and the Labour force survey (1983).

@@

For each scenario, I ran the model until 2028 with 10,000 parameter samples. I tested the difference between scenarios using the Mann-Whitney test for both the number of vaccines needed to prevent a single case in 15 years after vaccination for a cohort aged 13-14 years old at vaccination and the total number of additional notifications caused by ending the BCG schools' scheme. As in [@Sutherland1989] a 15 year time horizon was used with 5 year intervals. The year closest to the year of the change in vaccination policy (2005), which had model estimates, was used as the baseline. The code for this analysis is available online^[Code: https://github.com/seabbs/AssessBCGPolicyChange]

@@

The model produced results that were comparable with those from [@Sutherland1989] (Table \@ref(tab:model-validation); Table \@ref(tab:model-validation-2)). When estimating the total notifications from ending the BCG schools' scheme at different times in ethnic White UK born adults aged 15-29 years old in England and Wales the model had a median absolute error of `r median_lll_hhh_error` and a maximum absolute error of `r {pretty_max}` when compared to [@Sutherland1989]. I found that the percentage of cases in the first year was $f=0.764$ when fitted to the Sutherland et al. estimates using the least squares method.

@@

## Discussion

### 2019-07-16 rmds/06-tb-bcg-improv-outcomes.Rmd
updated table positions

To conduct this study, I first obtained all TB notifications for 2009-2015 in England from the Enhanced Tuberculosis surveillance (ETS) system (see Chapter \@ref(data)). I then considered five outcomes: All-cause mortality, death due to TB (in those who died), recurrent TB, pulmonary disease, and sputum smear status. I used logistic regression, with complete case analysis, to investigate each outcome with BCG vaccination, years since vaccination and age at vaccination, adjusting for potential confounders. All analyses were repeated using multiply imputed data. This work was supervised by Hannah Christensen and Ellen Brooks-Pollock. Collaborators at Public Health England including, Maeve K Lalor, Dominik Zenner, Colin Campbell, and Mary E Ramsay provided the data and commented on multiple versions of this work.

@@

I conducted sensitivity analyses to assess the robustness of the results, by dropping each confounding variable in turn and assessing the effect on the adjusted Odds Ratios (aORs) of the exposure variable. I repeated the analysis excluding duplicate recurrent cases, and restricting the study population to those eligible for the BCG schools scheme (defined as UK born cases that were aged 14 or over in 2004) to assess the comparability of the BCG vaccinated and unvaccinated populations. To mitigate the impact of missing data I used multiple imputation, with the MICE package.[@VanBuuren2011] I imputed 50 data sets (for 20 iterations) using ) using all outcome and explanatory variables included in the analysis as predictors along with Public Health England centre. The model results were pooled using the small sample method,[@Barnard1999] and effect sizes compared with those from the main analysis.

@@

outcome_demo_tab_bcg %>% 
  set_names(., c("Outcome", names(.)[-1])) %>% 
  kable(caption = "Outcomes for individuals in England notified with TB between 2009-2015,  stratified by BCG vaccination status.",
         booktabs = TRUE, escape = TRUE) %>% 
    column_spec(c(1), width = "2cm") %>% 
    add_indent(indents) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position")%>% 
    add_header_above(c(" " = 2, "BCG status" = 3)) %>% 
    add_footnote(label = c("{% all cases}(% complete within vaccine status)[% complete within category]",
 "* Death due to TB in those who died and where cause of death was known"
), notation = "none") %>% 
  {.}
```

@@

demo_tab_bcg %>% 
  set_names(., c("Confounder", names(.)[-1])) %>% 
  kable(caption = "Confounders for individuals in England notified with TB between 2009-2015,  stratified by BCG vaccination status.",
         booktabs = TRUE, escape = TRUE) %>% 
    column_spec(c(1), width = "2cm") %>% 
    add_indent(indents) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_header_above(c(" " = 2, "BCG status" = 3)) %>% 
    add_footnote(label = c("{% all cases}(% complete within vaccine status)[% complete within category]",
 "* Death due to TB in those who died and where cause of death was known"
), notation = "none") %>% 
  {.}
```

@@

bcg_mortality_tab  %>%
  set_names(c("Variable", "Total", "All-cause mortality", 
              "OR (95% CI)", "P-value",
              "aOR (95% CI)", "P-value")) %>% 
    kable(caption = "Summary of logistic regression model output with BCG vaccination as the exposure and all-cause mortality as the outcome.",
         booktabs = TRUE, escape = TRUE) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    column_spec(c(1), width = "2cm") %>% 
    add_indent(indents) %>% 
    kable_styling(font_size = 8) %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals,", "aOR (95% CI): adjusted odds ratios with 95% confidence intervals"), notation = "none") %>% 
  {.}
```

@@

table_var_outs[[1]] %>% 
  combine_model_data_sum(DataSum = ModelDataSum[[1]]) %>% 
    set_names(c('Outcome', 'BCG vaccinated', 'Cases**', 'Cases with outcome (%)', 'OR (95% CI)', 'P-value', 'Cases***', 'Cases with outcome (%)', 'aOR (95% CI)', 'P-value')) %>% 
    kable(caption = "Summary of associations between BCG vaccination and all outcomes",
         booktabs = TRUE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>% 
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                           "* Death due to TB in those who died and where cause of death was known",
                           "** Univariable sample size for outcomes ordered as in table (% of all cases) = 30746 (60%), 596 (23%), 33954 (66%), 34410 (67%), 13678 (26%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of all cases) = 25993 (50%), 506 (20%), 29086 (56%), 29379 (57%), 11718 (23%)"
), 
notation = "none") %>% 
  landscape() %>% 
    {.}
```

@@

table_var_outs[[2]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[2]]) %>% 
    set_names(c('Outcome', 'Years since BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(
      caption.short = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated.", 
      caption = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated. The baseline exposure is vaccination $\\leq 10$ years before diagnosis compared to vaccination $11+$ years before diagnosis. Deaths due to TB (in those who died) had insufficient data for effect sizes to be estimated in both the univariable and multivariable analysis",
          booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>%  
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                           "* Death due to TB in those who died and where cause of death was known",
                           "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape()
```

@@

table_var_outs[[3]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[3]]) %>% 
    set_names(c('Outcome', 'Age at BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(
      caption.short = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated.", 
      caption = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated - the baseline exposure is vaccination at birth compared to vaccination from 1 to < 12, 12 to < 16, and 16+ years of age.",
         booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>% 
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                            "* Death due to TB in those who died and where cause of death was known",
                            "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape() %>% 
  {.}
```

@@

  df %>% 
  kable(
        caption.short = caption.short,
        caption = caption,
        booktabs = TRUE, escape = escape) %>% 
  column_spec(c(1), width = "3cm") %>%
  add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
  kable_styling(latex_options = "hold_position")
}

@@

```{r 06-sens-table, message=FALSE, echo=FALSE, results='asis', warning=FALSE}
bcg_ass_main %>% 
  set_names(c('Study population', 'Outcome', 'BCG', 'OR (95% CI)', 'P-value', 'aOR (95% CI)', 'P-value')) %>% 
  kable(
    caption.short = "Summary of associations between BCG vaccination and all outcomes.", 
    caption = "Summary of associations between BCG vaccination and all outcomes; cases that have no recurrent flag in the ETS (n=50407), and cases that would have been eligible for the BCG schools scheme (n=9943). Those defined to be eligible for the schools scheme are the UK born, that were aged 14 or over in 2004", booktabs = TRUE) %>% 
    column_spec(c(1:2), width = "3cm") %>% 
    kable_styling(latex_options = "hold_position") %>%
    add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) %>% 
    kable_styling(font_size = 8)
```

>>>>

To conduct this study, I first obtained all TB notifications for 2009-2015 in England from the Enhanced Tuberculosis surveillance (ETS) system (see Chapter \@ref(data)). I then considered five outcomes: All-cause mortality, death due to TB (in those who died), recurrent TB, pulmonary disease, and sputum smear status. I used logistic regression, with complete case analysis, to investigate each outcome with BCG vaccination, years since vaccination and age at vaccination, adjusting for potential confounders. All analyses were repeated using multiply imputed data. This work was adapted from [@Abbott:2019ir] (also available as a preprint^[Preprint: https://doi.org/10.1101/366476]) supervised by Hannah Christensen and Ellen Brooks-Pollock. Collaborators at Public Health England including, Maeve K Lalor, Dominik Zenner, Colin Campbell, and Mary E Ramsay provided the data and commented on multiple versions of this paper.

@@

I conducted sensitivity analyses to assess the robustness of the results, by dropping each confounding variable in turn and assessing the effect on the adjusted Odds Ratios (aORs) of the exposure variable. I repeated the analysis excluding duplicate recurrent cases, and restricting the study population to those eligible for the BCG schools scheme (defined as UK born cases that were aged 14 or over in 2004) to assess the comparability of the BCG vaccinated and unvaccinated populations. To mitigate the impact of missing data I used multiple imputation, with the MICE package.[@VanBuuren2011] I imputed 50 data sets (for 20 iterations) using all outcome and explanatory variables included in the analysis as predictors along with Public Health England centre. The model results were pooled using the small sample method,[@Barnard1999] and effect sizes compared with those from the main analysis. All code for this analysis is available online^[Code: https://github.com/seabbs/ExploreBCGOnOutcomes].

@@

outcome_demo_tab_bcg %>% 
  set_names(., c("Outcome", names(.)[-1])) %>% 
  kable(caption = "Outcomes for individuals in England notified with TB between 2009-2015,  stratified by BCG vaccination status.",
         booktabs = TRUE, escape = TRUE) %>% 
    column_spec(c(1), width = "3cm") %>% 
    add_indent(indents) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "HOLD_position")%>% 
    add_header_above(c(" " = 2, "BCG status" = 3)) %>% 
    add_footnote(label = c("{% all cases}(% complete within vaccine status)[% complete within category]",
 "* Death due to TB in those who died and where cause of death was known"
), notation = "none") %>% 
  {.}
```

@@

demo_tab_bcg %>% 
  set_names(., c("Confounder", names(.)[-1])) %>% 
  kable(caption = "Confounders for individuals in England notified with TB between 2009-2015,  stratified by BCG vaccination status.",
         booktabs = TRUE, escape = TRUE) %>% 
    column_spec(c(1), width = "3cm") %>% 
    add_indent(indents) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "HOLD_position") %>% 
    add_header_above(c(" " = 2, "BCG status" = 3)) %>% 
    add_footnote(label = c("{% all cases}(% complete within vaccine status)[% complete within category]",
 "* Death due to TB in those who died and where cause of death was known"
), notation = "none") %>% 
  {.}
```

@@

bcg_mortality_tab  %>%
  set_names(c("Variable", "Total", "All-cause mortality", 
              "OR (95% CI)", "P-value",
              "aOR (95% CI)", "P-value")) %>% 
    kable(caption = "Summary of logistic regression model output with BCG vaccination as the exposure and all-cause mortality as the outcome.",
         booktabs = TRUE, escape = TRUE) %>% 
    kable_styling(latex_options = "HOLD_position") %>% 
    column_spec(c(1), width = "3cm") %>% 
    add_indent(indents) %>% 
    kable_styling(font_size = 8) %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals,", "aOR (95% CI): adjusted odds ratios with 95% confidence intervals"), notation = "none") %>% 
  {.}
```

@@

table_var_outs[[1]] %>% 
  combine_model_data_sum(DataSum = ModelDataSum[[1]]) %>% 
    set_names(c('Outcome', 'BCG vaccinated', 'Cases**', 'Cases with outcome (%)', 'OR (95% CI)', 'P-value', 'Cases***', 'Cases with outcome (%)', 'aOR (95% CI)', 'P-value')) %>% 
    kable(caption = "Summary of associations between BCG vaccination and all outcomes",
         booktabs = TRUE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>% 
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "HOLD_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                           "* Death due to TB in those who died and where cause of death was known",
                           "** Univariable sample size for outcomes ordered as in table (% of all cases) = 30746 (60%), 596 (23%), 33954 (66%), 34410 (67%), 13678 (26%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of all cases) = 25993 (50%), 506 (20%), 29086 (56%), 29379 (57%), 11718 (23%)"
), 
notation = "none") %>% 
  landscape() %>% 
    {.}
```

@@

table_var_outs[[2]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[2]]) %>% 
    set_names(c('Outcome', 'Years since BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(
      caption.short = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated.", 
      caption = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated. The baseline exposure is vaccination $\\leq 10$ years before diagnosis compared to vaccination $11+$ years before diagnosis. Deaths due to TB (in those who died) had insufficient data for effect sizes to be estimated in both the univariable and multivariable analysis",
          booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>%  
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "HOLD_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                           "* Death due to TB in those who died and where cause of death was known",
                           "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape()
```

@@

table_var_outs[[3]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[3]]) %>% 
    set_names(c('Outcome', 'Age at BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(
      caption.short = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated.", 
      caption = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated - the baseline exposure is vaccination at birth compared to vaccination from 1 to < 12, 12 to < 16, and 16+ years of age.",
         booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>% 
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "HOLD_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                            "* Death due to TB in those who died and where cause of death was known",
                            "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape() %>% 
  {.}
```

@@

  df %>% 
  kable(
        caption.short = caption.short,
        caption = caption,
        booktabs = TRUE, escape = escape) %>% 
  column_spec(c(1), width = "3cm") %>%
  add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
  kable_styling(latex_options = "HOLD_position")
}

@@

```{r 06-sens-table, message=FALSE, echo=FALSE, results='asis', warning=FALSE}
bcg_ass_main %>% 
  set_names(c('Study population', 'Outcome', 'BCG', 'OR (95% CI)', 'P-value', 'aOR (95% CI)', 'P-value')) %>% 
  kable(
    caption.short = "Summary of associations between BCG vaccination and all outcomes.", 
    caption = "Summary of associations between BCG vaccination and all outcomes; cases that have no recurrent flag in the ETS (n=50407), and cases that would have been eligible for the BCG schools scheme (n=9943). Those defined to be eligible for the schools scheme are the UK born, that were aged 14 or over in 2004", booktabs = TRUE) %>% 
    column_spec(c(1:2), width = "3cm") %>% 
    kable_styling(latex_options = "HOLD_position") %>%
    add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) %>% 
    kable_styling(font_size = 8)
```
